A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
strucutre

To estimate the complexity of the code being evaluated,
Fig.~\ref{fig:ast-size} shows the distribution of the abstract syntax tree
size of the \c{expr} argument to \eval. The majority of inputs across core
and packages (\miss{XX}\%) is 1. That is to say, the code being evaluated
consists of a single variable name or constant. A function call needs at
least three nodes. Inputs smaller than \c{X} nodes account for 95\% of all
calls. Sizes are roughly similar between core and packages.

@@

\subsection{How are they used}

- classify evals based on what they can be replaced with

\subsubsection{A taxonomy of \c{eval}}

@@

\subsubsection{\eval and environments}

@@

\subsection{How to replace evals}

@@

\subsection{How dangerous is eval}

\subsection{How many evals can be replaced}

>>>>

To roughly estimate the complexity of the code being evaluated,
Fig.~\ref{fig:ast-size} shows the distribution of the abstract syntax tree
size of the \c{expr} argument to \eval. The majority of inputs across core
and packages (\miss{XX}\%) is 1. That is to say, the code being evaluated
consists of a single variable name or constant. A function call needs at
least three nodes. Inputs smaller than \c{X} nodes account for 95\% of all
calls. Sizes are roughly similar between core and packages.

@@

{\bf Missing from this section is the measure of the number of events
  happening in an eval}

\section{A taxonomy of eval}

@@

\subsection{Operation mix}

Here we should show some information about what happens during an eval. What kinds of operations...

@@

\subsection{Scope}

Here we talk about scopes and envs

\subsection{Patterns}

Here we categorize evals in some common groups

\subsection{Provenance}

Here we talk about where the input of an eval comes from

\subsection{Consistency}

Here we talk about whether the same call site sees the same pattern

{\bf Polymorphic may not be the right word.}

@@
